\sysfull

### 2017-08-08 paper/relatedwork.tex
Related Work-subsection 2 placeholder

\noindent \textbf{Intermittent Execution Environments:} Checkpoint runtimes include DINO~\cite{dino}, Hibernus/Hibernus++~\cite{hibernus,hibernusplusplus}. The only available Task-based intermittent runtime systems are Chain~\cite{chain} and Alpaca~\cite{alpaca}. \sys goes beyond what any task-based system performed by providing \emph{automatic} task creation and \emph{adaptivity} to energy state and energy storage \emph{obliviousness} of the compiled code. \todo{complete this section}{Przemek}

>>>>

\noindent \textbf{Intermittent Execution Environments:} Earlier work include Dewdrop~\cite{dewdrop} (splitting task such that they fill-in the capacitor). Similar, specific-application tailored system includes Wisent and Stork~\cite{stork,wisent}. Checkpoint runtimes include DINO~\cite{dino}, Quickrecall~\cite{quickrecall}, Hibernus/Hibernus++~\cite{hibernus,hibernusplusplus} are checkpointing-based systems requiring hardware support to measure remaining storage energy---a feature prohibitive given typical high energy cost expenditure of such hardware. The only available Task-based intermittent runtime systems are Chain~\cite{chain} and Alpaca~\cite{alpaca}. \sys goes beyond what any task-based system performed by providing \emph{automatic} task creation and \emph{adaptivity} to energy state and energy storage \emph{obliviousness} of the compiled code. \todo{complete this section}{Przemek}
